Pillar 1 - Sequential Pattern Mining

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
include data loading in set up section for clarity
compute descriptive stats at the Academic Year (e.g. 2018-2019) level instead of Year_numerical (e.g. 2017) level.

# Load data
We load the environment `data_pillar1` which we saved at the end of the data preparation. It contains the data sets `d_course` and `d_transcript`.
```{r loading data}
load("Output/data_general.RDATA")
load("Output/data_pillar_1.RDATA")
```

# Set up

@@

# Year level
statistics$year <- provide_statistics(Year_numerical)

@@

For convenience:
```{r for convenience II}

```

>>>>

# Set up
We load the environment `data_pillar1` which we saved at the end of the data preparation. It contains the data sets `d_course` and `d_transcript`.
```{r loading data}
load("Output/data_general.RDATA")
load("Output/data_pillar_1.RDATA")
```

@@

# Year level
statistics$year <- provide_statistics(`Academic Year`)

@@
